Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-04-30 paper.tex
update

\author{Chris Peikert\cite{Author1}, Yared Afework\cite{Author2}}

@@

% If changing the name of the bib file, change \bibliography{test} at the bottom
\begin{filecontents}{sources.bib}

@misc{Author1,
  author       = "Peikert, Chris",
  howpublished = "\url{mailto:cpeikert@umich.edu}",
}

@misc{Author2,
  author       = "Efrem Afework, Yared",
  howpublished = "\url{mailto:yared.efremafework@algorand.foundation}",
}

@article{BIP32-Ed25519,
  author  = "Khovratovich, Dmitry, and Law, Jason",
  title   = "BIP32-Ed25519 Hierarchical Deterministic Keys over a Non-linear Keyspace",
  year    = "2017",
  journal = "IEEE European Symposium on Security and Privacy Workshops (EuroS&PW)",
  note    = "\url{https://ieeexplore.ieee.org/abstract/document/7966967}",
}

\end{filecontents}

@@

Bitcoin relies on the Secp256k1 elliptic curve, which has a linear key space. A new public key can be formed by adding $[x]B$ to the public key $[k]B$, where $x$ and $k$ are private keys/scalars and $B$ the base point. This results in a new public key whose private key is $[x] + [k]$ (mod the order of the finite field).

@@

Ed25519 has a number of advanta\usepackage[skip=10pt]{parskip}ges, such as high speed constant-time implementations and a signing procedure where the nonce is deterministically derived from the data to be signed (mitigating the kind of attack that Sony PS3 suffered).

@@

- Bits 0, 1, 2:  set to 0, ensuring that the key is a multiple of 8 and avoiding small subgroup attacks.
- Bit 255: set to 1, to ensuring the Montgommery ladder computation used in scalar multiplication takes constant time.
- Bit 254: set to 0, ensuring the key is in the range of the field order ($2^{255} - 19$).

@@

>>>>

\author{Chris Peikert\cite{Author1}, Yared Efrem Afework\cite{Author2}, Bruno Martins\cite{Author3}}

@@

@@

Bitcoin relies on the Secp256k1 elliptic curve, which has a linear key space. A new public key can be formed by adding $[x]B$ to the public key $[k]B$, where $x$ and $k$ are private keys/scalars and $B$ the base point. This results in a new public key whose private key is $[x] + [k] mod q$ for $q$ the order of the field.

@@

Ed25519 has a number of advantages, such as high speed constant-time implementations and a signing procedure where the nonce is deterministically derived from the data to be signed (mitigating the kind of attack that Sony PS3 suffered).

@@

\begin{itemize}
  \item Bits 0, 1, 2:  set to 0, ensuring that the key is a multiple of 8 and avoiding small subgroup attacks.
  \item Bit 254: set to 1, to ensuring the Montgommery ladder computation used in scalar multiplication runs in constant time.
  \item Bit 255: set to 0, ensuring the key is in the range of the field order ($2^{255} - 19$).
\end{itemize}

@@

\section{Implementations}

The suggestions provided in this paper have been implemented as part of the ARC52 Bip32-Ed25519 libraries provided by the Algorand Foundation.

\begin{itemize}
  \item \href{https://github.com/algorandfoundation/bip32-ed25519-kotlin}{Kotlin}
  \item \href{https://github.com/algorandfoundation/bip32-ed25519-swift}{Swift}
  \item \href{https://github.com/algorandfoundation/bip32-ed25519-ts}{TypeScript}
\end{itemize}
